RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-03-06 inst/doc/pubs/README.Rmd
update README

```{r echo=FALSE}
library(knitr)
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
```

>>>>

```{r echo=FALSE}
library(knitr)
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE)
```
